### 2023-10-09 main.tex
N2

>>>>

\textbf{Remark}: In case of $N=2$ we can introduce $q=\sum_{x=1}^{L}\delta_{\tau_{x},1}$. Moreover, we call $\ell_{1},\ldots,\ell_{q}$ the coordinates where particles of type $1$ are present. Thus, the coefficient of the above formula can be written as
&\frac{\Gamma\left(2+\sum_{x=1}^{L}\delta_{\tau_{x},N}\right)}{\Gamma\left(2+L\right)}\left(\prod_{x=1}^{L}\left[\lambda_{\tau_{x}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},1}\right)\right]^{1-\delta_{\tau_{x},N}}\right)%=\lambda_{1}^{q}\prod_{x=1}^{L}\left(2+L-y_{x}-\sum_{j=x}^{L}\delta_{\tau_{j},1}\right)^{\delta_{\tau_{x},1}}
=\lambda_{1}^{q}\prod_{k=1}^{q}\frac{\left(1+L-\ell_{k}-\sum_{j=k+1}^{q}\delta_{\tau_{x_{j}},1}\right)}{(2+L-k)}
Moreover, for each $q\in \{1,\ldots,L\}$ we introduce the coordinates $1\leq\ell_{1}<\ldots,\ell_{q}\leq L$ and, by varying $q$, we have a one-to-one mapping with $\bm{\tau}$. Therefore, we can write 
	|\Psi^{''}\rangle=\sum_{q=0}^{L}\lambda_{1}^{k}\sum_{1\leq \ell_{1}<\ldots<\ell_{q}\leq L}\prod_{k=1}^{q}\frac{\left(1+L-\ell_{k}-q+k\right)}{(2+L-k)}|\bm{\ell},q\rangle
